Teaching a Class to Grade Itself using Game Theory

### 2013-09-08 Primes Write up.tex
Got rid of we

\subsection{Rules}
Grading one of the assignments costs 1 unit of effort, and will always find the correct score, \emph{i.e} the \emph{objective score}, and grading is the only way to find this objective score.
\subsection{Assumptions}
These are the assumptions that we have made in creating this model.

@@

This model is quite unrealistic, but not by such a degree that it is unimaginable. We were, however, able to create a perfect solution if the problem took place in this situation.

\subsection{Mechanism}
In the model, we have the professor grade one paper, called \emph{X}. The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper. Every student is also given a copy of \emph{X}.

@@

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
\subsection{Results}
The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, we get a value of 2.
The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.

\subsection{Problems}
The goal for this model was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand. We now have a model that works very well in an unrealistic scenario, so we decided that this solution was fine, and moved on to a new model.

@@

This provides a very different scenario than the original model, because now students will be able to figure out which papers are calibrated. However, we still wanted to try and generalize the previous solution and apply it to the new model, so we came up with the following scheme.

@@

\subsection{Problems}
The major problem with this method is the amount of work. The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students. For this reason we tried to come up with a different mechanism.

\section{The Deduction Model}
In the new mechanism, we went with a completely different strategy, that we wanted to work better than the previous one.

@@

\subsection{Problems}
Although the result that we produced for the previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative. This means that we need to find a different solution to the same problem which encourages a kind of positive competition, instead of the negatives formed by trying to find the most mistakes

\section{The Flag Model}
For the next mechanism, we kept all of the assumptions the same, and simply tried to find a way to better the feeling of negative competition.
\subsection{Mechanism}
Start by having each paper get graded by two people. Then, the original writer of this paper chooses which of the two grades he / she would like to have, and looks over the justifications for losing any points on both papers. If they see that any of these justifications are incorrect, they flag the paper and send it to the professor. Following this, the paper they chose to have is sent to a third party, who grades the paper, and checks if their grade is close to the one that was given to the paper. If it isn't, the paper is sent to the professor. After everything that needs to be flagged has been, the professor grades all the flagged papers, and rewards people who were correct with a 2 point bonus. If no papers from any group were flagged, every grader in that group gets two points. Final grades are whatever the person chose if there was no flagging, or whatever the professor gave them if there was.
\subsection{Why it Works}
To find out how efficient this mechanism is, we need to analyze two things:
1) Is everyone an honest flagger?
$$$$
2) Do the graders grade honestly
\subsubsection{Flagging}
There are two cases for this:

>>>>

\subsection{Rules}
Grading one of the assignments costs 1 unit of effort, and will always find the correct score, \emph{i.e} the \emph{objective score}, and grading is the only way to find this objective score.
\subsection{Assumptions}
These are the assumptions that were made in creating this model.

@@

This model is quite unrealistic, but not by such a degree that it is unimaginable. Because of this, it was possible to create a perfect solution if the problem took place in this situation.

\subsection{Mechanism}
In the model, the professor grades one paper, called \emph{X}. The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper. Every student is also given a copy of \emph{X}.

@@

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
\subsection{Results}
The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.

\subsection{Problems}
The goal for this model was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand. There is now a model that works very well in an unrealistic scenario, so we moved on to a new model.

@@

This provides a very different scenario than the original model, because now students will be able to figure out which papers are calibrated. However, it would be better to try and generalize the previous solution and apply it to the new model, which leads to the following scheme.

@@

\subsection{Problems}
The major problem with this method is the amount of work. The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students. For this reason a different mechanism was necessary.

\section{The Deduction Model}
In the new mechanism, a different strategy was created; one that would ideally work better than the previous ones.

@@

\subsection{Problems}
Although the result that was produced for the previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative. This means that finding a different solution to the same problem was necessary, in which students are placed in positive competition, instead of the negative one formed by trying to find the most mistakes

\section{The Flag Model}
For the next mechanism, all of the assumptions were kept the same, and simply tried to find a way to better the feeling of negative competition.
\subsection{Mechanism}
Start by having each paper get graded by two people. Then, the original writer of this paper chooses which of the two grades he / she would like to have, and looks over the justifications for losing any points on both papers. If they see that any of these justifications are incorrect, they flag the paper and send it to the professor. Following this, the paper they chose to have is sent to a third party, who grades the paper, and checks if their grade is close to the one that was given to the paper. If it isn't, the paper is sent to the professor. After everything that needs to be flagged has been, the professor grades all the flagged papers, and rewards people who were correct with a 2 point bonus. If no papers from any group were flagged, every grader in that group gets two points. Final grades are whatever the person chose if there was no flagging, or whatever the professor gave them if there was.
\subsection{Why it Works}
To find out how efficient this mechanism is, two things needed to be analyzed:
1) Is everyone an honest flagger?
$$$$
2) Do the graders grade honestly
\subsubsection{Flagging}
There are two cases for this:
